The shape of dark matter halos in the AURIGA simulations

### 2019-02-19 Paper/paper.tex
edit

Figure \ref{fig:triax_DM} summarizes this comparizon for all 30 halos
in the Level 3 simulations. 
Measurements at $R_{\rm vir}/16$ are represented by circlse while squares 
are measurements at $R_{\rm vir}$. 
All halos, except two, show that outer regions rounder than inner
regions.
The exceptions are cases where a merging substructures near  the
halo's center give rise to perturbed axial ratios measurments. 
Figure \ref{fig:triax_HDM} shows the same information, this time for
the MHD simulations. 
The main radial trend continues to hold, albeit less pronounced; halos
in MHD simulations are in general rounder than their DM counterparts
and the increased roundness in outer regions is less pronounced on
average.

In Table \ref{table:median_axial_ratio_DM} and Table \ref{table:median_axial_ratio_MHD}
we summarize the results for the median values of the axis ratio in
the two sets of simulations (DM and MHD). 
The lower/upper bounds correspond to the first/third quartiles. 
The values in Table  \ref{table:median_axial_ratio_DM} shows how halos are
monotonically rounder with increasing radius, while the comparison
against Table \ref{table:median_axial_ratio_MHD} shows that halo are
consistently rounder in MHD simulations at every radius.

@@

Concerning MHD halos, \textit{prescindible?(((the expected tendency is
  not clear. Some studies claim that the DM halo must be oblate, at
  least in the vicinities of the disk, to ensure its stability
  . However,)))} not much is said about its
dependence with radius as previous studies focus rather on the effects
of baryons on the dynamics of the halo at fixed radii. Examining the
representative behaviour of a MHD halo on figure \ref{fig:DM_MHD},
some things are noticeable: first, the DM halo is almost perfectly
oblate around $\approx 10-30$kpc, second, its axial ratio $b/a$ start
decreasing very slowly after $50kpc$ and below $10kpc$ and third, its
axial ratio $c/a$ does not exhibit noticeable change in the whole
radial domain. (Pass from representative case to averaged values)
These results are statistically supported and sumarized on table
\ref{MHD table} and figure \ref{fig:Triax_MHD}

>>>>

Figure \ref{fig:triax_DM} summarizes this comparizon for all 30 halos
in the Level 3 simulations. 
Measurements at $R_{\rm vir}/16$ are represented by circlse while squares 
are measurements at $R_{\rm vir}$. 
All halos, except two, show that outer regions rounder than inner
regions.
The exceptions are cases where a merging substructures near  the
halo's center give rise to perturbed axial ratios measurments. 
Figure \ref{fig:triax_HDM} shows the same information, this time for
the MHD simulations. 
The main radial trend continues to hold, albeit less pronounced; halos
in MHD simulations are in general rounder than their DM counterparts
and the increased roundness in outer regions is less pronounced on
average.
This average behaviour is more clear in the individual case of Halo 16
in Figure \ref{fig:triaxial_ratios}. There, as we mentioned, at the virial radius the halo is
rounder than its DM counterpart. 
Going from $50$\kpch to
$10$ \kpch radii the $b/a$ ratio is constant almost close to unity
while it decreases to $0.5$ in DM-only simulation

the DM halo is almost perfectly
oblate around $\approx 10-30$kpc, second, its axial ratio $b/a$ start
decreasing very slowly after $50kpc$ and below $10kpc$ and third, its
axial ratio $c/a$ does not exhibit noticeable change in the whole
radial domain. (Pass from representative case to averaged values)
These results are statistically supported and sumarized on table
\ref{MHD table} and figure \ref{fig:Triax_MHD}

In Table \ref{table:median_axial_ratio_DM} and Table \ref{table:median_axial_ratio_MHD}
we summarize these results for the median values of the axis ratio in
the two sets of simulations (DM and MHD). 
The lower/upper bounds correspond to the first/third quartiles. 
Summarizing: a) Table  \ref{table:median_axial_ratio_DM} shows how halos are
monotonically rounder with increasing radius; b) the comparison
against Table \ref{table:median_axial_ratio_MHD} shows  how DM halos
are consistently rounder in MHD simulations than DM-only runs at every radius.

@@
